\documentclass[11pt,a4paper]{article}

% --- PACKAGES AND SETUP ---
\usepackage[margin=0.75in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{hyperref}

% --- CUSTOM DEFINITIONS ---

% Define custom colors from your CV for consistency
\definecolor{sectioncolor}{RGB}{0,102,204} % Professional blue
\definecolor{darkgrey}{gray}{0.5}          % For secondary text

% Custom command for author emphasis
\newcommand{\myname}[1]{{\color{sectioncolor}\textbf{#1}}}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=darkgrey,
    urlcolor=darkgrey,
    citecolor=darkgrey,
    pdftitle={Yash Bhusare - Publication List},
    pdfauthor={Yash Bhusare}
}

% List spacing
\setlist[itemize]{itemsep=0.8em, topsep=0.5em, label=\textbullet, leftmargin=*}

% --- DOCUMENT ---

\begin{document}

\pagestyle{empty}

\begin{center}
    {\Huge\bfseries\color{sectioncolor}Yash Bhusare} \\[0.2em]
    {\large\itshape Publication List}
\end{center}
\vspace{0.5em}\hrule\vspace{1.5em}

\section*{Publications}
\begin{itemize}
    \item \textbf{Low-frequency Probes of the Persistent Radio Sources Associated with Repeating Fast Radio Bursts} \\
    {\color{darkgrey}\myname{Bhusare, Y.}, Maan, Y., \& Kumar, A.} \\
    {\color{darkgrey}\href{https://ui.adsabs.harvard.edu/abs/2025ApJ...993..234B}{\textit{ApJ}, 993, 234 (2025)}}

    \item \textbf{The Second CHIME/FRB Catalog of Fast Radio Bursts} \\
    {\color{darkgrey}CHIME/FRB Collaboration (inc. \myname{Bhusare, Y.})} \\
    {\color{darkgrey}\href{https://arxiv.org/abs/2601.09399}{\textit{arXiv:2601.09399}} (2026)}

    \item \textbf{Long-term monitoring of repeating FRB 20220912A with the uGMRT at low radio frequencies} \\
    {\color{darkgrey}Kumar, A., Maan, Y., Lal, B., \myname{Bhusare, Y.}, et al.} \\
    {\color{darkgrey}\href{https://arxiv.org/abs/2512.21889}{\textit{arXiv:2512.21889}} (2025)}

    \item \textbf{FRB 20250316A: A Brilliant and Nearby One-off Fast Radio Burst Localized to 13 pc Precision} \\
    {\color{darkgrey}CHIME/FRB Collaboration (inc. \myname{Bhusare, Y.})} \\
    {\color{darkgrey}\href{https://ui.adsabs.harvard.edu/abs/2025ApJ...989L..48C}{\textit{ApJL}, 989, L48 (2025)}}

    \item \textbf{Varying Activity and the Burst Properties of FRB 20240114A Probed with GMRT Down to 300 MHz} \\
    {\color{darkgrey}Kumar, A., Maan, Y., \& \myname{Bhusare, Y.}} \\
    {\color{darkgrey}\href{https://ui.adsabs.harvard.edu/abs/2024ApJ...977..177K}{\textit{ApJ}, 977, 177 (2024)}}
\end{itemize}

\section*{Astronomer's Telegrams}
\begin{itemize}
    \item \textbf{Detection of bursts from FRB 20250613A down to 300 MHz with uGMRT} \\
    {\color{darkgrey}\myname{Bhusare, Y.}, Maan, Y., Kumar, A., et al.} \\
    {\color{darkgrey}\href{https://www.astronomerstelegram.org/?read=17274}{\textit{ATel \#17274}} (2025)}

    \item \textbf{Detection of a potential persistent radio source associated with FRB 20240114A} \\
    {\color{darkgrey}\myname{Bhusare, Y.}, Maan, Y., \& Kumar, A.} \\
    {\color{darkgrey}\href{https://www.astronomerstelegram.org/?read=16820}{\textit{ATel \#16820}} (2024)}

    \item \textbf{uGMRT detection of more than a hundred bursts from FRB 20220912A in 300 - 750 MHz frequency range} \\
    {\color{darkgrey}\myname{Bhusare, Y.}, Kumar, A., Maan, Y., et al.} \\
    {\color{darkgrey}\href{https://www.astronomerstelegram.org/?read=15806}{\textit{ATel \#15806}} (2022)}

    \item \textbf{Non-Detection of Radio Emission from Magnetar CXOU J164710.2-455216} \\
    {\color{darkgrey}Lal, B., \myname{Bhusare, Y.}, Kumar, A., et al.} \\
    {\color{darkgrey}\href{https://www.astronomerstelegram.org/?read=17599}{\textit{ATel \#17599}} (2026)}

    \item \textbf{Non-detection of bursts from the repeating FRB 20251130A and upper limit on the associated PRS with uGMRT follow-up observations} \\
    {\color{darkgrey}Kumar, A., \myname{Bhusare, Y.}, Maan, Y., et al.} \\
    {\color{darkgrey}\href{https://www.astronomerstelegram.org/?read=17596}{\textit{ATel \#17596}} (2026)}

    \item \textbf{Non-detection at 1.26 GHz of persistent radio source associated with the repeating FRB 20230607A} \\
    {\color{darkgrey}Pelliciari, D., Bruno, L., \myname{Bhusare, Y.}, et al.} \\
    {\color{darkgrey}\href{https://www.astronomerstelegram.org/?read=17230}{\textit{ATel \#17230}} (2025)}

    \item \textbf{GMRT detection of high activity from FRB 20240619D at 650 MHz} \\
    {\color{darkgrey}Kumar, A., Panda, U., \myname{Bhusare, Y.}, et al.} \\
    {\color{darkgrey}\href{https://www.astronomerstelegram.org/?read=16745}{\textit{ATel \#16745}} (2024)}

    \item \textbf{Detection of low radio frequency bursts from FRB 20240114A with GMRT and upper limits on any associated PRS} \\
    {\color{darkgrey}Kumar, A., Maan, Y., \& \myname{Bhusare, Y.}} \\
    {\color{darkgrey}\href{https://www.astronomerstelegram.org/?read=16452}{\textit{ATel \#16452}} (2024)}
\end{itemize}

\end{document}